`infercnv` results exploration for `r params$sample_id`

### 2024-11-12 analyses/cell-type-wilms-tumor-06/notebook_template/06_cnv_infercnv_exploration.Rmd

---
title: "`infercnv` results exploration for `r params$sample_id`"
author: "Maud PLASCHKA"
date: "`r Sys.Date()`"
params:
  scpca_project_id: "SCPCP000006"
  sample_id: "SCPCS000184"
  seed: 12345
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

  #### CNV score
  meta <- infercnv_obj@meta.data |>
    mutate(has_cnv_score = rowSums(meta[, grepl("has_cnv_chr", colnames(meta))])) |>
    mutate(has_cnv_score = case_when(
      has_cnv_score > cnv_threshold ~ "CNV",
      has_cnv_score <= cnv_threshold ~ "no CNV"
    ))

>>>>

---
title: "`infercnv` results exploration for `r params$sample_id`"
author: "Maud PLASCHKA"
date: "`r Sys.Date()`"
params:
  scpca_project_id: "SCPCP000006"
  sample_id: "SCPCS000179"
  seed: 12345
output: 
  html_document: 
    toc: yes
    toc_float: yes
    code_folding: hide
    highlight: pygments
    df_print: paged
---

@@

  #### CNV score
  meta <- infercnv_obj@meta.data
  meta <- meta |>
    dplyr::mutate(has_cnv_score = rowSums(meta[, grepl("has_cnv_chr", colnames(meta))])) |>
    dplyr::mutate(has_cnv_score = dplyr::case_when(
      has_cnv_score > cnv_threshold ~ "CNV",
      has_cnv_score <= cnv_threshold ~ "no CNV"
    ))
